MCC Models

### 2020-09-21 papers/full_paper/manuscript.Rmd
update supplement for revision

library("papaja")
library(tidyverse)
library(knitr)
library(ggthemes)
library(langcog)
library(rwebppl)
library(matrixStats)
library(coda)
#library(ggpubr)
library(lme4)
library(broom)
library(broom.mixed)
library(readxl)
library(lsr)

@@

We did not model the social-cognitive processes that specify the probability of an object being the referent given common ground - we simply measured it empirically. As a consequence, our approach treats common ground as equivalent to more basic manipulations of contextual salience [e.g. in @frank2012predicting]. Thus, our model would not differentiate between a situation in which an object would be salient because it has been the focus of an interaction and one in which it would be more salient because it was big or colorful. Our model also does not take into account the important distinction for psycholinguistics, namely the difference between privileged ground vs. common ground. This distinction has been addressed computationally by Heller and colleagues [@heller2016perspective; @mozuraitis2018modeling]. In their work, they focus on how listeners identify the referent of ambiguous referring expressions. Their probabilistic model simultaneously considers the (differing) perspectives of both interlocutors and trades off between them. In principle, the model of Heller and colleagues [-@heller2016perspective] and the *integration model* could be combined with one another to address how privileged vs common ground trades off with other pragmatic information.

>>>>

library("papaja")
library(tidyverse)
library(knitr)
library(ggthemes)
library(langcog)
library(matrixStats)
library(coda)
#library(ggpubr)
library(lme4)
library(broom)
library(broom.mixed)
library(readxl)
library(lsr)

@@

We did not model the social-cognitive processes that specify the probability of an object being the referent given common ground - we simply measured it empirically. As a consequence, our approach treats common ground as equivalent to more basic manipulations of contextual salience [e.g. in @frank2012predicting]. Thus, our model would not differentiate between a situation in which an object would be salient because it has been the focus of an interaction and one in which it would be more salient because it was big or colorful. Based on a process model of common ground, one could further specify how common ground information (i.e. social context) interacts with other contextual information [@degen2015wonky; @tessler2017warm]. Relatedly, our model does not take into account the important distinction for psycholinguistics, namely the difference between privileged ground vs. common ground. This distinction has been addressed computationally by Heller and colleagues [@heller2016perspective; @mozuraitis2018modeling]. In their work, they focus on how listeners identify the referent of ambiguous referring expressions. Their probabilistic model simultaneously considers the (differing) perspectives of both interlocutors and trades off between them. In principle, the model of Heller and colleagues [-@heller2016perspective] and the *integration model* could be combined with one another to address how privileged vs common ground trades off with other pragmatic information.
